%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      {\small#1} & {\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Shivaji Reddy} \\ \vspace{1pt} 
    \smallskip
    \small 1170 Tripoli St, Riverside, California 92507 \\
    
    \small +14088964549 $|$ \href{mailto:x@x.com}{sdont002@ucr.edu} $|$ 
    \href{https://www.linkedin.com/in/shivaji-reddy-042/}{linkedin.com/shivaji-reddy-042} $|$
    \href{https://github.com/ShivajiReddy}{github.com/ShivajiReddy}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Riverside}{Sept 2021 -- May 2023}
      {MS, Computer Science}{GPA: 4.0/4.0}
    \resumeSubheading
      {Manipal Institute of Technology}{July 2016 -- June 2020}
      {Bachelor of Technology, Computer Science}{}
  \resumeSubHeadingListEnd

 %-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C++, Java, Kotlin, C, Swift, Python, Bash} \\
     \textbf{Frameworks and Databases: }{Spring, Android, Spring Boot, NodeJS, Selenium, JSOUP, Hadoop, Terraform} \\
     \textbf{Software Development}{:Agile, Scrum, SDLC, Rest API, JUnit, JIRA, Data scraping} \\
     \textbf{Developer Tools}{: Linux, AWS, Git, Github, Postman, Microservices, Docker} 
    }}
 \end{itemize}



%-----------EXPERIENCE-----------
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------


\section{Experience}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Software Engineer Intern}{June 2022 -- Present}
      {Esri}{Redlands, California}
      \resumeItemListStart
        \resumeItem{Designing an Image Comparison framework within ArcGIS Android SDK for Esri Maps that aims to handle, analyze and rectify Map rendering failures across the application suite.}
        \resumeItem{Contributing to the new Open Source Kotlin Android Applications with latest Map Enhancements and visualisations.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Graduate Teaching Assistant -- Advanced Operating Systems}{March 2022 - Present}
      {University of California, Riverside}{Riverside, California}
      \resumeItemListStart
        \resumeItem{Conducted Programming Sessions and guided a Graduate class of 60 students through a series of Kernel Programming problems in xv6 OS on System calls, Scheduling Algorithms, Deadlock Prevention, and Multi-threading.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{July 2020 -- July 2021}
      {Cardinal Health}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Engaged in the Costco Pharmacy Application team that is responsible for the continuous development and maintenance for an in-production product, affecting 10M+ users in the US.}
        \resumeItem{Designed and developed key features like ability to register for Flushots, contact-less package pickups, locker delivery.}
        \resumeItem{Worked on a third-party API integration module that fused Costco Pharmacy into Instacart increasing the user traffic by over 20\%.}
        \resumeItem{Managed periodic integration of core product functionalities into Costco application with 100\% success rate.}
        \resumeItem{Tech Stack: Java, Spring, Springboot, AWS, Terraform, JDBC, MySQL}
      \resumeItemListEnd
      
    \resumeSubheading
      {Software Engineer Intern}{Jan 2020 -- June 2020}
      {Cardinal Health}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Deployed a centralized full-stack web application using Spring, React, SQL and Docker to analyze and handle failed CRON jobs across 100+ client applications of the organization increasing the response time by over 5x.}
        \resumeItem{Structured a new product deployment cycle using Terraform scripts to launch and auto-scale AWS Instances.}
    \resumeItemListEnd

    \resumeSubheading
      {Summer Research Intern}{May 2018 -- July 2018}
      {International Institute of Technology (IIIT)}{Hyderabad, India}
      \resumeItemListStart
        \resumeItem{Designed a configurable 360-degree evaluation system to analyze brain responses that is currently in use to conduct various studies in the Cognitive Science lab.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{TV Series Search Engine} $|$ \emph{Java, Hadoop, Jsoup, Lucene, MongoDB, Node JS, React JS}}{Nov 2022}
          \resumeItemListStart
            \resumeItem{Built a Google-like Search engine that ranks relevant information by scraping data from Wikipedia pages using a multi-threaded web-crawler and indexing them using Lucene and Hadoop MapReduce with a React UI.}
          \resumeItemListEnd
      
      \resumeProjectHeading
          {\textbf{Job Scheduler Dashboard} $|$ \emph{Java, Spring, SQL, AWS, Jenkins, Terraform}}{June 2020}
          \resumeItemListStart
            \resumeItem{Designed and Deployed a central dashboard that acts as a one-point application to monitor, analyze and handle various  CronJobs for all pharmacy clients in the company product.}
            \resumeItem{Key features: Re-trigger failed jobs at once, Creation of new jobs in bulk, Fetch Job, job-history visulization.}
          \resumeItemListEnd


 
      \resumeProjectHeading
          {\textbf{XV6 Thread Library} $|$ \emph{Java, Android}}{Nov 2018}
          \resumeItemListStart
            \resumeItem{Created an Android app for freshmen, where time tables of all the freshman classes can be easily accessed offline. Received over 250+ Google Playstore installs within 24hours of launching}
          \resumeItemListEnd        
     
    \resumeSubHeadingListEnd



%


%-------------------------------------------
\end{document}

